EE454 Project 1 Report

### 2015-09-23 p1/report/latex/draft.tex
fixed merge with master conflict in heading

\graphicspath{ {../} }

@@

\section{Performance Evaluation}
\subsection{Results}
	The following results were the outcome of classifying images as the class associated with the highest probability in the probability vector.
\begin{center}
	\includegraphics[scale=0.8]{confusionmatrix}
	~\\~\\

@@

@@

\section{Member Contributions}

>>>>

\usepackage{titlesec}
\graphicspath{ {../} }

\newcommand{\sectionbreak}{\clearpage}

@@

\section{Performance Evaluation}
\subsection{Results}
	The following results were the outcome of classifying images as the class associated with the highest probability in the probability vector.
\begin{center}
	\includegraphics[scale=0.7]{confusionmatrix}
	~\\~\\

@@

~\\~\\
\noindent
All of the exploratory images we used were either taken by us or were taken from Google Images. The code we used to read in the exploratory images can be found in 'getAllFiles.m' and 'getTrueClass.m'. We produced the results above by running the 10 images through the function found in 'NeuralNet.m' and classifying the images by assigning the image the class associated with the highest probability. The classification process was done manually.

@@

~\\~\\
The code used to produce the results found in this section can be found in 'exploratory\_main.m'.

\section{Member Contributions}
	Overall the contributions made form each team member were pretty even. Whenever the team met to work on the project most of the team members were in attendance. Everyone who was in attendance at each team meeting attempted to work on a different piece of the project to ensure that we were making steady progress. The coding was not split up evenly as one team member did not attend the initial meeting and as a result he missed most of the actual coding and basically all of the design decisions. We attempted to split the report up evenly, but as the deadline approached scheduling meetings became difficult and some individuals were unavailable to work on the report. In conclusion, the work was not split up evenly among our four group members, but everyone attempted to contribute.
